---
title: "hw_200"
author: "simaaq"
date: "2019-10-20"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction
## Hooke's Law demo. A spring experiment is carried out twice. Spring 1 and spring 2 are loaded with 0, 1, 2, ..., 9 equal weights and their lengths are measured. Each record contains the index, weight, spring 1 length and spring 2 length. There is also an initial header line.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
location <- "https://people.sc.fsu.edu/~jburkardt/data/csv/hooke.csv"
data <- read.csv(location)
summary(data,title="hooke")
```

## below is the descpritve statistics for the two columns from the dataset, the descriptive1 shows the statistics of spring1 data and descriptive2 shows the statistics of spring2 data. The mean value for spring1 is 2.205 and the mean value for spring2 is 0.14880
```{r}
descriptive1 <- data[[2]]
descriptive2 <- data[[3]]
summary(descriptive1)
summary(descriptive2)
```


##Here is the plot of all the data
```{r}
plot(data)
```
##Here is the plot of the relationship between mass and spring1
```{r}
head(data)
plot(data$Mass..kg., data$Spring.1..m., xlab = "mass", ylab = "spring1")
```

##Here is the plot of the relationship between mass and spring2
```{r}
plot(data$Mass..kg., data$Spring.2..m., xlab = "mass", ylab = "spring2")
```

##Here is the plot of the relationship between spring1 and spring2
```{r}
plot(data$Spring.1..m., data$Spring.2..m., xlab = "spring1", ylab = "spring2")
```

##Below is the simple linear regression between spring1 and spring2
```{r linearmodel}
spring1 = data$Spring.1..m.
spring2 = data$Spring.2..m.

reg<- lm(spring1~spring2)
plot(spring1,spring2, col="red", main = "spring1 and spring2 Regression", abline(reg), cex = 1.3, pch= 16, xlab = "spring1 length", ylab= "spring2 length")
summary(reg)

res<-residuals(reg)
mean(res)
median(res)
plot(res)
reg
print(summary(reg))
```
##From the statistics above, we will see that the median residual is `r median(res)`. This number is very small. Thus the relationship between the spring one and two is not that important. 


